---
title: "Slide with R by Xarigan package"
author: "Kazu Nozue"
date: "2018/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    #css: ["default.css","my-theme.css"]
    css: "default.css"
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
<style>
.small-code3 code.r {
   color: magenta;
  font-size: 0.7em;
}
#header1 {
  color: blue;
}
.header2 h1 {
  color: purple;
  font-size: 1.5em;
}
code.r{ /* Code block */
    font-size: 1em;
    color: green;
}
</style>
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = TRUE,error=TRUE)
```
---

<large>prerequisite_large</large> 
prerequisite_normal
<small>prerequisite_small</small>
* All above work.
```{r}
library(edgeR);library(tidyverse);library(readr);library(readxl)
```
---
class: center
# control code chunk appearance (chunk option did not work)
```{r, cols.print=1,rows.print=1}
mtcars
```
---
# control code chunk appearance2
test
```{r, size="small"}
mtcars
```
---
class: header2, small-code3
# control code chunk appearance3 using class: header2, small-code3
```{r, out.width=3}
mtcars
```
